MSHS COVID-19 Vaccinations

### 2021-04-14 Evening-Huddle-Stats.Rmd
Update reference file pod mapping to remove MSQ duplicates.

# Import reference data for site and pod mappings
site_mappings <- read_excel(paste0(user_directory, "/ScheduleData/",
                                   "Automation Ref 2021-04-07.xlsx"),
                            sheet = "Site Mappings")
pod_mappings <- read_excel(paste0(user_directory, "/ScheduleData/",
                                  "Automation Ref 2021-04-07.xlsx"),
                           sheet = "Pod Mappings Simple")

>>>>

# Import reference data for site and pod mappings
site_mappings <- read_excel(paste0(user_directory, "/ScheduleData/",
                                   "Automation Ref 2021-04-14.xlsx"),
                            sheet = "Site Mappings")
pod_mappings <- read_excel(paste0(user_directory, "/ScheduleData/",
                                  "Automation Ref 2021-04-14.xlsx"),
                           sheet = "Pod Mappings Simple")
